|

### 2021-11-19 07-Chp-Triangulation.Rmd
End of day:

@@

Convience functions in the `triangulate` package (see Section \@ref(tri-software)) were used to preprocess risk of bias data for use with both bias-direction plots and adjusted meta-analyses, as discussed in subsequent sections. These bias direction plots themselves were created using the risk-of-bias visualisation tool described in Appendix \ref(?).

@@

<!-- TODO Deal with the fact that the Panel wasn't super useful -->

@@

@@

@@

@@

@@

@@

A key issue in this analysis is t

As observed from Figure \@ref(@) in the bias-adjusted analysis, the Ostergaard _et al._ 2017

>>>>

<!-- TODO The additive biases in this example figure should refer to favouring the comparator, meaning that the bias is pulling towards the intervention side (i.e. is making the comparator look better). -->

@@

Convenience functions in the `triangulate` package (see Section \@ref(tri-software)) were used to preprocess risk of bias data for use with both bias-direction plots and adjusted meta-analyses, as discussed in subsequent sections. These bias direction plots themselves were created using the risk-of-bias visualisation tool described in Appendix \ref(?).

@@

<!-- TODO Sensitivity analysis - set means to zero and only adjust for variance. Essentially adding uncertainty based on the amount of bias but not moving the effect estimate -->

@@

In this study, there were 3 domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result.

In Domain 1, the study did not adjust for ApoE4, which is predicted to mask any true assocation between statins and . As such, the bias is predicted to _favour the comparator_ and so the absolu

In Domain 5, there was a moderate risk of differential miclassification on the basis of the exposure, and so the predicted direction of bias in this domain is to _favours the intervention_. As such, the absolute direction of bias is to the left.

For consistency with the other NRSI, in the absence of a protocol, bias in the selection of the reported result is assumed to be _away from the null_. Given the position of the effect estimate below the null (`r hold()`), the absolute direction of bias in this domain is to the left.

@@

<!-- Question - Hypercholesterolemia should not be included here, as it is focused on total cholesterol rather than specifically LDL-c, right? -->

@@

<!-- TODO How effect are fibrates at lowering triglycerides? is it a direct effect, or are there alternative -->

@@

#### Case study: effect of triglycerides at midlife on vascular dementia

@@

In future, domain specific. In fact, it may also be more reasonable for domains such as confounding to adjust on a per-confounder basis. In the approach, prior distributions are assigned to each of the confounding domains prespecified as part of the ROBINS-I tool. Then, rather than assigning a domain level distrbution based on an arbraty judgement of how many important confounders are missing, the result is adjusted for each confounder not accounted for in the original analysis. As an example, ApoE4 is a much stronger confounder of the LDL-c than a single lifestyle indicator.

<!-- TODO Talk about sensitivity analysis that only added variance rather than moving the point estimate, and highlight that this is a way to account for bias without having to make strong predictions about the direction of bias in a given domain. -->

Estimates of modifying means might be conservative in relation to some potentially strong confounders. A previous simulation study estimated that ApoE4 would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021a]

@@

A key issue in this analysis is the subjectivity of both the

Key problem here is if the rigourness of the tools is not equivalent. This is less of an issue for the ROB suite of tools (RoB 2.0, ROBINS-I, ROBINS-E). This can be illustrated by the Ostergaard _et al._ study having low risk of bias.

This is particularly problematic given the default of the ROBINS-I and ROBINS-E tool to require a "Moderate" judgement in the confounding domain. It means that, if the MR tool is insufficiently assessing bias in MR studies, the best performed cohort study (low risk of bias across everything other that confounding) will  always downweighted versus potentialyl a poor MR study.

Similarly,

### 2021-11-19 08-Discussion.Rmd
End of day:

This chapter

## Chapter overview

In this chapter I will summarise the principal findings from my thesis,

assess the unique contributions of this thesis to the field of research,

discuss the implications for both clinical and public health policy,

describe the overall strengths and limitations of this thesis as a whole,

suggest avenues for impactful future research based on my findings and experiences.

<!-- In this final chapter I will: -->
<!--  Summarise the main findings from each chapter in relation to my two thesis hypotheses. -->
<!-- Chapter 6: Discussion -->
<!-- 162 -->
<!--  Discuss the similarities and differences between my findings and the published literature. -->
<!--  Critically evaluate the novel contributions and implications of my research. -->
<!--  Describe the limitations of my studies and consider what I would do differently given what I have learnt. -->
<!--  Recommend avenues for future research. -->

@@

## Summary of principal findings

Given the detailed discussion

@@

## New evidence

Found slight raised risk of dementia in CPRD patients () with higher LDL-c measured at midlife, driven by the finding for Alzheimer's disease [@iwagami2021]. Not inconsistent with the findings presented in this thesis

@@

There are

@@

@@

@@

Containerisation was used to ensure that the code is reproducible, in line iwht best practices

@@

Several avenues for future research, buiding on the work presented here,

###

@@

Preprints also represent a key oppportunity to assess the impact of peer review on qualitivative changes within

@@

As discussed, there is an absence of evidence on vascular dementia across the evidence base, potentially driven y

@@

@@

### Reviewing of Mendelian randomisation studies

As a field, and as noted in Chapter \@ref(sys-rev-heading-results), the evidence synthesis theory and methods have not been sufficient developed for Mendelian randomisation studies. Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g. genetic instrumental variable analysis.)

Work is ongoing in this field, and new methodological work such as the release of teh MR-STROBE guidelines will aid in the future assessing by helping to improve the reporting of Mendelian randomisation studies.

Problems with reporting of MR studies will hopefully

@@

### Imporved analytical designs

>>>>

This chapter details the

## Introduction

The aim of this thesis was to attempt to infer the causal effect of blood lipid levels on dementia outcomes.

In this chapter I will summarise the principal findings from my thesis, assess the unique contributions of this thesis to the field of research, discuss the implications for both clinical and public health policy, describe the overall strengths and limitations of this thesis as a whole, suggest avenues for impactful future research based on my findings and experiences.

In __Chapter \@ref(sys-rev-tools-heading)__ presents a new tool for the systematic searching of health-related preprints, and detail

In __Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)__ describe the methods and results of a comprehensive systematic review of the relationship between blood lipids (and treatments that modify them) and dementia outcomes.

In __Chapter \@ref(cprd-heading)__ presents an analysis of lipid-regulating use and dementia outcomes in the CPRD, a large scale

In __Chapter \@ref(ipd-heading)__ presents an individual patient data meta-analysis, using previously unanalysed data accessed via the Dementia Platform UK.

In __Chapter \@ref(tri-heading)__ presents a narrative summary of the evidence identified and produced by the preceding chapters, and proposes a new method of systematically integration of multiple evidence sources as part of quantitative triangulation exercise.

@@

## New evidence produced

Since the systematic review was performed, there have been some notable further analysis related to the central thesis question here. Two of these are discussed here notable studies are discussed here.

Found slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease [@iwagami2021]. Not inconsistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.

<!-- TODO The study says that simulated effect of ApoE4 is a 1.09 RR in the absence of a true causal effect. Main results are between 1.03 and 1.17. CI for most extreme results is (lower = 1.08) is not inconsistent with the effect introduced by ApoE4 which is just a single confounder out of many -->

In relation to the suggestion in this analysis that raised triglycerides were associated with an increasede risk of vascular dementia, a 2021 study in a  125,727 Danish participants found the moderate hypertriglyceridemia was associated with increased risk of non-Alzheimer's dementia (`r estimate(1.79, 1.16,2.87,"HR")`).[@nordestgaard2021]

@@

@@

As part

In hindsight, the decision to take a broad approach to inclusion of dementia outcomes potentially resulted in larger workload than anticipated, particularly when considered evidence from across different study designs. In a do-over, I would have considered a single dementia outcome.

Additionally, in hindsight, I may have considered a mor. However, under the conditions of my grant, the scope for chang

As a reflective process throughout the PhD, I maintained a catalogue of failures (available in Appendix \@ref(appendix-catalogue-failures)).

@@

The strengths a limitations of each component of this thesis are discussed in the respective chapters. Here I highlight the strengths and weakness of the thesis as a body of work.

@@

__Strengths__
- New evidence sources for an under-studied condition
- Development of new methods and tool

__Weaknesses__
A general limitation of this thesis is the absence of known results/data. This occured in both the systematic review, via the selection of reporting results and potential for publication bias. It was also observeed.

These facts both potentially bias the summary associations observed here, in addition to weakening the precision of the estimates produced.

- Confounding by indication

- A lot of UK based data

@@

Unfortunately, given the. However, as discussed in other chapters of this thesis and elsewhere, sharing of analysis code is a useful step towards transparency when the underlying datasets are not readily available.

@@

Several avenues for future research, building on the work presented here, are possible.

@@

Preprints also represent a key opportunity to assess the impact of peer review on qualitative changes within

@@

As discussed, there is an absence of evidence on vascular dementia across the evidence base, potentially driven (for NRSI) at the leasby a publication

@@

This is particularly relevant given that there was some evidence for an association of hypertriglyceraecia with vascular dementia. Future research should explicitly examine this relationship as part o f wider exploration of vascular disease.

@@

### Viewing of Mendelian randomisation studies

As noted in Chapter \@ref(sys-rev-heading-results), evidence synthesis theory and methods have not been sufficient developed for the inclusion of Mendelian randomisation studies.

A key issue arises from the lack of an established risk of bias tool, which adds uncertainty to the accuracy of risk-of-bias assessments which can influence future work based on them, as discussed in Chapter \@ref(7). In addition, a lack of guidance around whether the inclusion of two-sample Mendelian randomisation studies using identical summary statistics. This was illustrated in detail in Chapter \@ref(4), where XXX studies using the same , and meta-analysing these as independent effect estimates would provide an overly precise result. Finally, future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g. genetic instrumental variable analysis).

Synthesis of Mendelian randomisation studies is not helped by the varied (and often poor) reporting, though the recent release of the STROBE-MR reporting guidelines should go someway to addressing this.

@@

### Triangulation

The field of quantitative triangulation is one ripe for future work. In the first instance, guidance

Finally, methods for the standardisation of meth

### 2021-11-19 front-and-back-matter/99-appendices.Rmd
End of day
End of day:

<!----------------------------------------------------------------------------->
### Section 2

@@

<!----------------------------------------------------------------------------->
### Catalogue of failures

Short section detailing the things I tried to do but which did not work.

@@

\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}

>>>>

@@

<!----------------------------------------------------------------------------->
### Catalogue of failures {#appendix-catalogue-failures}

Short section detailing the things I tried to do but which did not work:

failing to realise that the initial codelist used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))

@@

\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
